### 2012-01-02 doc/theses/mikula/proposed_algorithm.tex
Master thesis: In progress.

\chapter{Proposed Algorithm}
\todo[inline]{Nejaky uvod a zkratke hrnutie}
\todo[inline]{Lexikalna a syntakticka analyza z diplomky J. Schejbala}
\todo[inline]{Staticka analyza typov vyrazov}
\todo[inline]{Predpoklad korektnosti dotazov}

@@

\todo[inline]{Tady z těch try a probably je jasně vidět, že netušíte co vlastně přesně algoritmus bude dělat. Nejdříve si to rozmyslete, pak pište text. Rozhodně by se takové výrazy neměly v DP dobjevovat, působít o velmi nedůvěryhodně. Měl by to být strohý popis toho, co bylo uděláno.}

@@

A simple algorithm is presented in Algorithm \ref{ALG_processing_of_functions} \todo{Q: uvadzat aj taketo jednoduche funkcie? A: Obecně by mělo být popsáno vše. Ale pokud se nějaká jednoduchá věc např. opakuje, tak stačí napsat, že je algoritmus podobný jako v předchozím případě nebo tak něco.}. It uses \texttt{getFunctionDeclarationNodes()} function, defined in Algorithm \ref{ALG_retrieval_of_function_declaration_nodes}, which returns a list of all function declaration nodes in the syntax three. Actually, it does not have to search the whole syntax tree as the function declaration nodes can be present only in the query prolog section.

@@

@@

\todo[inline]{Popisat dvojicu funkcii memorizeType() a getType(). Taktiez trojicu set(), get(), add().}

@@

>>>>

\chapter{Proposed Algorithm}
\todo[inline]{Nejaky uvod a zkratke hrnutie}
\todo[inline]{Predpoklad korektnosti dotazov}

@@

@@

A simple algorithm is presented in Algorithm \ref{ALG_processing_of_functions}. It uses \texttt{getFunctionDeclarationNodes()} function, defined in Algorithm \ref{ALG_retrieval_of_function_declaration_nodes}, which returns a list of all function declaration nodes in the syntax three. Actually, it does not have to search the whole syntax tree as the function declaration nodes can be present only in the query prolog section.

@@

\subsection{Auxiliary Functions}
Before proceeding to the next phase of the algorithm, we introduce auxiliary functions used in pseudo algorithms.

Function $memorizeType()$ takes two arguments $node$ and $type$ and it memorizes the given type of the specified expression node. This information can be then retrieved by function $getType()$, specifying the particular node as its argument.

Another group consists of functions $set()$, $add()$, and $get()$. Function $set()$ memorizes a given value of a specified property of a specified node. It is used to assign a node with a named value, for example, $set(someNode, color, 'red')$ will assign $someNode$ with string value $'red'$ wich can be then retrieved by function $get()$, specifying the node and the property name. For example, $get(someNode, color)$ returns $'red'$. A subsequent call of $set()$ assigning a node with a value of already assigned property will overwrite it, leaving the property with the newer value. However, a property can has several values and this can be achieved using function $add()$ with the same syntax as function $set()$ but instead of overwriting the existing property, $add()$ will append the new value to the existing ones. Then, a call of $get()$ on this node and property returns a list of all its values, preserving the order of their addition.

@@

@@

\section{Step 4: Key Discovery}
